### 2016-11-28 README.Rmd
better tests and README

In this example, we fit a random forest to the Boston housing data. Note, for any of the following examples, you can see a progress bar by simply specifying `.progress = "text"` in the call to `partial`.
```{r, message = FALSE, warning=FALSE}
# Load required packages
library(ggmap)  # for plotting data on maps
library(pdp)  # for constructing PDPs
library(randomForest)  # for random forest algorithm

@@

# The partial function allows for multiple predictors
partial(boston.rf, pred.var = c("lstat", "rm"), grid.resolution = 10,
        plot = TRUE, chull = TRUE)

# The plotPartial function offers more flexible plotting
pd <- partial(boston.rf, pred.var = c("lstat", "rm"), grid.resolution = 10)

@@

Finally, we demonstrate the seemless interface between the `pdp` package and the `caret` package. For illustration we use `caret`'s `train` function to tune a support vector machine (SVM) with a radial basis function kernel to the Pima Indians diabtes data. We then cinstruct PDPs from the final model for the most "important" variables. When training a model using `caret`'s `train` function, you can view tuning progress by setting `verboseIter = TRUE` in the call to `trainControl`.
```{r, message=FALSE, warning=FALSE}
# Load required packages
library(caret)  # for model training/tuning

>>>>

In this example, we fit a random forest to the Boston housing data. Note, for any of the following examples, you can see a progress bar by simply specifying `.progress = "text"` in the call to `partial`. You may also reduce the computation time via the `grid.resolution` option in the call to `partial`.
```{r, message = FALSE, warning=FALSE}
# Load required packages
library(ggmap)  # for plotting data on maps
library(pdp)  # for constructing PDPs
library(randomForest)  # for random forest algorithm

@@

# The partial function allows for multiple predictors
partial(boston.rf, pred.var = c("lstat", "rm"), plot = TRUE, chull = TRUE)

# The plotPartial function offers more flexible plotting
pd <- partial(boston.rf, pred.var = c("lstat", "rm"))

@@

Finally, we demonstrate the seamless interface between the `pdp` package and the `caret` package; `caret` is an extremetly useful package for classification and regression training that, essentially, has one function (`train`) for fitting all kinds of predictive models in R (e.g., `glmnet`, `svm`, `xgboost`, etc.). For illustration we use `caret`'s `train` function to tune a support vector machine (SVM) with a radial basis function kernel to the Pima Indians diabetes data. We then construct PDPs from the final model for the most "important" variables. When training a model using `caret`'s `train` function, you can view tuning progress by setting `verboseIter = TRUE` in the call to `trainControl`.
```{r, message=FALSE, warning=FALSE}
# Load required packages
library(caret)  # for model training/tuning
